Plot Results

### 2023-10-10 code/ResultsPlots.Rmd

pdf(file = "TWAS_qq.pdf")
qq(Assoc$TWAS.P, bty='n', las=1)
dev.off()
```

@@

# Store SVA results
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_Manhattan.pdf', name = 'Twas Gene Association Manhattan Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'Manhattan Plot'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

@@

>>>>

p <- ggplot(don, aes(x=BPcum, y=-log10(TWAS.P))) +

    # Custom the theme:
    theme_bw() +
    theme( 
      legend.position="none",
      panel.border = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )
ggsave("TWAS_Manhattan.eps",p)

pdf(file = "TWAS_qq.pdf")
qq(Assoc$TWAS.P, bty='n', las=1)
dev.off()

setEPS()
postscript("TWAS_qq.eps", onefile = TRUE)
qq(Assoc$TWAS.P, bty='n', las=1)
dev.off()

@@

# PDFs
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_Manhattan.pdf', name = 'Twas Gene Association Manhattan Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'Manhattan Plot'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

@@

# PDFs
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_Manhattan.eps', name = 'Twas Gene Association Manhattan Plot EPS', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataType = "eps"
  all.annotations$dataSubType = 'Manhattan Plot'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_qq.eps', name = 'Twas Gene Association QQ-Plot EPS', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataType = "eps"
  all.annotations$dataSubType = 'QQ-Plot'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
